\section*{Preamble}
After three and a half years of studying at Hoschule Bonn-Rhein-Sieg, this elaboration is the final step. I am thankful for all the knowledge I could get during this time. I would do it again at any time. \\ 

Thank you, Prof. Kaul and Prof. Alda. You made it possible to write about such an exciting topic. Not only is this topic in my interest, but also a hot topic in the current market  situation. This fact helped carry me through the writing—furthermore, the support during the thesis kept me on track with the elaboration. \\
As well, I want to say thank you to all the reviewers of my thesis. Thank you, Marc, Alex, and Jan, for your steady input and feedback. \\
A special thank you to my girlfriend, Marie. You were why I finally started with my Master's and kept pushing to finish it. But not only that, the moral support and all the exam preparation during those three years. \\
I also want to say thank you to my family. They were always on my side, supportive, and made it possible to follow this education path. \\
I received exceptional support, which is not guaranteed, from my manager at LeanIX. Guido was always supportive in case of working hours and always kept my back free from other topics during my elaboration. \\
And I also want to thank all the people who talked with me about my thesis topic and gave me different perspectives to analyze. \\
Finally, I want to thank my writing chair in the living room. It supported my back several hours of thinking, coding, and writing this thesis, as well as the dartboard next to it, which was always a suitable break between the Chapters.\\

With these words said, I hope I did not forget anyone on my journey and that the reader of this enjoys my thesis as I did writing it. \\

\begin{flushright}
Kind regards,\\
Tom
\end{flushright}
