\newpage
\section{The \acl{SDS}}\label{saas_design_system}
This chapter presents the implementation of the newly created design system as a standard for the web user interfaces for SaaS products. \\
Modeling the architecture of a new design system is the first step. Looking at existing design systems and trying to understand how they work and extract requirements in order to develop a common system that fits most products in the SaaS world. \\
Then, this chapter presents the actual implementation of a component, including the technology stack used and the creation process. \\
The chapter concludes with an explanation of the build chain. How the build process bundles all the components and atoms to make them usable for any project. At the end, an example shows the possibilities to integrate the finished bundle into existing software.\\
Modeling the architecture of a system that supports customization of SaaS product user interfaces is not a trivial task. Most of the time, user interface design serves only one product. However, the goal of \ac{SDS} is to find common ground for multiple products in one domain. \\
Design systems define a common place where the company's products can align. Why is it impossible to develop a central system to create a common idea for user-friendly SaaS products? Not only do well-designed components help align, but a design system foundation with guidelines and principles helps developers and designers create a good product. \\

\input{chapter_3/requirements}
\input{chapter_3/modeling}
\input{chapter_3/component_implementation}
\input{chapter_3/integration}